### 2021-07-20 newvariant.tex
done

\begin{figure}[!th]
\begin{center}
\includegraphics[width=0.95\textwidth]{control_sim.pdf}
\caption{
\textbf{Simulations of constant-strength and constant-speed interventions.}
Constant-strength (A--C) and constant-speed (D--F) interventions are simulated using the renewal equation (see Supplementary Materials for details of simulations).
(A,D) Daily incidence of infections caused by the wild type ($\iw(t)$, gray) and the variant ($\iv(t)$, colored).
(B,E) Instantaneous reproduction number of the variant $\Rv(t)$ calculated using \eref{instR}.
(C,F) Proportion of incidence of infections caused by the variant ($\iv(t)/(\iw(t)+\iv(t))$) on a logit scale. 
Epidemic trajectories are calculated assuming $\rw=0\pday$, $\delta=0.1\pday$, $\rv=0.1\pday$, $\Gy{wt}=5\,\textrm{days}$, and $\kappa=1/5$ for pre-intervention conditions, and then introducing constant-strength and constant-speed interventions on day 30.
The pre-intervention ratio between the mean generation interval $\Gy{var}/\Gy{wt}$ is assumed to equal 1.5 (longer), 1 (equal), and 1/1.5 (shorter) for three different scenarios.
The constant-strength and constant-speed interventions are identically modeled as illustrated in \fref{strengthspeed}.
}
\label{fig:control_sim}
\end{center}
\end{figure}

@@

In contrast, epidemic trajectories under the constant-speed intervention look identical regardless of the mean generation interval of the variant (\fref{control_sim}D). 
As shown in \fref{strengthspeed}E, a constant-speed intervention leads to greater reduction in $\Rv(t)$ when the mean generation-interval of the variant is longer (\fref{control_sim}E).
In this case, the relative speed of the variant also remains unaffected by the constant-speed intervention because the epidemic speed of the wild type $\rw$ and the variant $\rv$ are both reduced by equal amounts $\phi$, resulting in the post-intervention epidemic speed of $\rw-\phi$ and $\rv-\phi$, respectively.

>>>>

\begin{figure}[!th]
\begin{center}
\includegraphics[width=0.95\textwidth]{control_sim.pdf}
\caption{
\textbf{Simulations of constant-strength and constant-speed interventions.}
Constant-strength (A--C) and constant-speed (D--F) interventions are simulated using the renewal equation (see Supplementary Materials for details of simulations).
(A,D) Daily incidence of infections caused by the wild type ($\iw(t)$, gray) and the variant ($\iv(t)$, colored).
(B,E) Instantaneous reproduction number of the variant $\Rv(t)$ calculated using \eref{instR}.
(C,F) Proportion of incidence of infections caused by the variant on a logit scale. 
Epidemic trajectories are calculated assuming $\rw=0\pday$, $\delta=0.1\pday$, $\rv=0.1\pday$, $\Gy{wt}=5\,\textrm{days}$, and $\kappa=1/5$ for pre-intervention conditions, and then introducing constant-strength and constant-speed interventions on day 30.
The pre-intervention ratio between the mean generation interval $\Gy{var}/\Gy{wt}$ is assumed to equal 1.5 (longer), 1 (equal), and 1/1.5 (shorter) for three different scenarios.
The constant-strength and constant-speed interventions are identically modeled as illustrated in \fref{strengthspeed}.
}
\label{fig:control_sim}
\end{center}
\end{figure}

@@

In contrast, epidemic trajectories under the constant-speed intervention look identical regardless of the mean generation interval of the variant (\fref{control_sim}D). 
As shown in \fref{strengthspeed}E, a constant-speed intervention leads to greater reduction in $\Rv(t)$ when the mean generation-interval of the variant is longer (\fref{control_sim}E)---
this implies a change in relative strength $\rho$ because the effectiveness of a constant-speed intervention is sensitive to the generation-interval distribution.
In this case, the relative speed of the variant remains unaffected by the constant-speed intervention because the epidemic speed of the wild type $\rw$ and the variant $\rv$ are both reduced by equal amounts $\phi$, resulting in the post-intervention epidemic speed of $\rw-\phi$ and $\rv-\phi$, respectively.
